Automated Topic Naming

### 2012-04-08 ese/ese.tex
- [X] Validity on authors         Although briefly noted in the validity section, the two most         frequent committers may be defining the global distribution of         NFR topics in Pg, if, for example they have produced the bulk         of commits for the topic extraction. This, perhaps, could be         mentioned earlier with a fraction of commits these two authors         produced.      - In section {RQ3: Do Different Developers Work on Different        NFRs?} we added text that showed the proportions of the top 3        authors and later mentioned this domination of the the global

A topic analysis tool such as LDA will try to find $N$ independent
word distributions within the word distributions of all input
messages. 
If there are not $N$ independent word distributions, the topics
produced tend to be duplicates of each other, that is, they share the
top terms. During this study we found that if we used a value of 20
for $N$, duplicate topics were infrequent in MaxDB and MySQL. The
PostgreSQL study was added later and we followed the same methodology
to extract topics fro PostgreSQL, the choice of $N$ = 20 was not
necessarily the optimal choice for PostgreSQL.
Linear combinations of these $N$ word distributions are meant to represent and recreate the word distributions of any of the original messages. In other words, these topics are cross-cutting collections of words relevant to one or more of our commit messages. 
LDA extracts topics in an unsupervised manner; the algorithm relies
solely on the source data and word distributions of messages, with no human intervention.
%We applied Blei's LDA implementation~\cite{Blei2003} against the word distributions of these commits, and generated lists of topics per period.

@@

%\subsection{Timeline analysis}
Topic time-lines are depicted in Figures \ref{fig:mysql-timeline}, 
\ref{fig:maxdb-timeline} and \ref{fig:pgsql-timeline}. These topic time-lines show the
temporal patterns of NFR frequencies.
%NEIL- I think this (below) is just confusing, although maybe important to note.
This is generated from the manually annotated
topics, although this visualization can be generated from the
results of labelled topic extraction. Note that there are no unlabelled topics in this data-set.

@@

%data/clusters.R

@@

Figure \ref{fig:authorcluster} shows that when we use $6$-clusters, 
\texttt{petere}, one of the major contributors, is in his own cluster
while two other major contributors, \texttt{tgl} and \texttt{momjian}
form their own cluster (i.e., they are distant from one another in the
7-dimensional space). 
%NEIL - not sure the relevance of this ... needs more explaining. --> (they are also the most frequent committers). 
This is interesting because it means that the important developers
have different proportions of NFR-relevant contributions; they have different
focuses during development. In terms of the 2-clusters, we can see that \texttt{momjian}
and \texttt{tgl} are in the same cluster, but \texttt{petere} is
not. The most frequent committers do not share the same clusters, even
at the coarsest level of clustering, 2 clusters.  This implies that developers in
this sample do work on different sets of NFRs and have different
software quality focuses.

% NEIL --> Explain the reason why this sentence is included: 
%It should be noted that much of PostgreSQL development originates from
%the project mailing list, and the developers are often pushing integrations. 
If we compare the global NFR distribution (that is, the relative global frequency of each NFR label)
to each author we find that 25\%
 of the authors have a similarity (Pearson correlation) of $0.47$ or less. In other words, for these authors (gathered to the lower left of Figure  \ref{fig:authorsim}),
 their NFR distribution does not match well with the global
 distribution.
Authors \texttt{momjian} and \texttt{tgl} are in the top right of
Figure \ref{fig:authorsim}, dominate in topic count and commit count, and so are
    very similar to the global distribution of NFR topics.
Figure \ref{fig:authorsim} demonstrates that although a  few authors dominate in
the number of commits, many authors exhibit different behaviour in
terms of the NFR-relevant topics of their commits. Furthermore, there
are no authors in the top left corner, indicating that the authors who
commit less, do not contribute with a similar NFR-topic distribution
as \texttt{momjian} or \texttt{tgl}.
We found that number of commits correlated with an author's similarity to the
global NFR distribution ($0.59$ Pearson), i.e., the variables ``number of topics associated with a developer'' and ``number of commits'' are not discriminative.

>>>>

A topic analysis tool such as LDA will try to find $N$ independent
word distributions within the word distributions of all input
messages. 
If there are not $N$ independent word distributions, the topics
produced tend to be duplicates of each other, that is, they share the
top terms. During this study we found that if we used a value of 20
for $N$, duplicate topics were infrequent in MaxDB and MySQL. 
Sometimes LDA produces topics that have a
very low association to documents, and in this paper we removed topics
that
exhibit very low document association. Our threshold for
topic inclusion was that a topic needed to be related to at least 1
document with a gamma (the variational
posterior Dirichlet~\cite{Blei2003} of a topic to a document, similar
to an association weight) of $1.0$ or greater.
The
PostgreSQL study was added later and we followed the same methodology
to extract topics fro PostgreSQL, the choice of $N = 20$ was not
necessarily the optimal choice for PostgreSQL.
Linear combinations of these $N$ word distributions are meant to represent and recreate the word distributions of any of the original messages. In other words, these topics are cross-cutting collections of words relevant to one or more of our commit messages. 
LDA extracts topics in an unsupervised manner; the algorithm relies
solely on the source data and word distributions of messages, with no human intervention.
%We applied Blei's LDA implementation~\cite{Blei2003} against the word distributions of these commits, and generated lists of topics per period.

@@

%\subsection{Timeline analysis}
Topic time-lines are depicted in Figures \ref{fig:mysql-timeline}, 
\ref{fig:maxdb-timeline} and \ref{fig:pgsql-timeline}. These topic time-lines show the
temporal patterns of NFR frequencies.
%NEIL- I think this (below) is just confusing, although maybe important to note.
This is generated from the manually annotated
topics, although this visualization can be generated from the
results of labelled topic extraction. Note that there are no
unlabelled topics in this data-set. Furthermore these plots are
display data about the interpretation of NFRs relevant to topics;
different annotators might produce different results.

@@

%data/clusters.R
%hindle1@burn:~/oldhome/projects/query1-data/postgresql$ sort -u query1.mrs2 | egrep "\|200[234]\-[0-9]" | awk -F: '{print $1}' | sort | uniq -c > ~/projects/lda-paper/ese/authors.csv

@@

% > tmp/ts
% [1] 0.8601498
% > tm/ts
% [1] 0.7855114

Figure \ref{fig:authorcluster} shows that when we use $6$-clusters, 
\texttt{petere}, one of the major contributors, is in his own cluster
while two other major contributors, \texttt{tgl} and \texttt{momjian}
form their own cluster (i.e., they are distant from one another in the
7-dimensional space). 
\texttt{tgl} and \texttt{momjian} make up $79\%$ of the commits, and
together \texttt{tgl}, \texttt{momjian} and \texttt{petere} make up
$86\%$ of all commits.
%NEIL - not sure the relevance of this ... needs more explaining. --> (they are also the most frequent committers). 
This is interesting because it means that the important developers
have different proportions of NFR-relevant contributions; they have different
focuses during development. In terms of the 2-clusters, we can see that \texttt{momjian}
and \texttt{tgl} are in the same cluster, but \texttt{petere} is
not. The most frequent committers do not share the same clusters, even
at the coarsest level of clustering, 2 clusters.  This implies that developers in
this sample do work on different sets of NFRs and have different
software quality focuses.

% NEIL --> Explain the reason why this sentence is included: 
%It should be noted that much of PostgreSQL development originates from
%the project mailing list, and the developers are often pushing integrations. 
If we compare the global NFR distribution (that is, the relative global frequency of each NFR label)
to each author we find that 25\%
 of the authors have a similarity (Pearson correlation) of $0.47$ or less. In other words, for these authors (gathered to the lower left of Figure  \ref{fig:authorsim}),
 their NFR distribution does not match well with the global
 distribution.
As stated before, the  3 most frequent authors produced $86\%$ of the
commits and thus they dominate the global NFR distribution.
Authors \texttt{momjian} and \texttt{tgl} are in the top right of
Figure \ref{fig:authorsim}, dominate in topic count and commit count, and so are
    very similar to the global distribution of NFR topics.
Figure \ref{fig:authorsim} demonstrates that although a  few authors dominate in
the number of commits, many authors exhibit different behaviour in
terms of the NFR-relevant topics of their commits. Furthermore, there
are no authors in the top left corner, indicating that the authors who
commit less, do not contribute with a similar NFR-topic distribution
as \texttt{momjian} or \texttt{tgl}.
We found that number of commits correlated with an author's similarity to the
global NFR distribution ($0.59$ Pearson), i.e., the variables ``number of topics associated with a developer'' and ``number of commits'' are not discriminative.
